GLOBALIZER: A NOVEL SUPERCOMPUTER SOFTWARE SYSTEM FOR SOLVING TIME-CONSUMING GLOBAL OPTIMIZATION PROBLEMS

### 2016-08-09 2016/GOM/paper.tex
Update references in GOM paper

\item GlobSol (Kearfott, R. B., 2009) is oriented towards solving global optimization problems as well as

@@

\item LINDO (Lin, Y., Schrage.L., 2009) is features by a wide spectrum of problem solving mehtods which
it can be used for – these include linear, integer, stochastic, nonlinear, and global

@@

problems (see, for example, (Egorov, I. N., Kretinin, G. V., Leshchenko, I. A., Kuptzov, S. V., 2002)). The system is widely used to

@@

\item MATLAB Global Optimization Toolkit (see, for example, (Venkataraman, P., 2009)) includes a wide spectrum

@@

TOMLAB system (see, for example, (Holmström, K., Edvall, M. M., 2004)), which is an additional extension the widely-used MATLAB.

@@

integer programming and global optimization problems using the branch and bound method (Sahinidis, N. V., 1996).
BARON is included in the GAMS (General Algebraic Modeling System) system used extensively – see (Bussieck, M. R., Meeraus, A., 2004).

@@

implemented in the R language (see, for example, (Mullen, K. M., 2014)). Among these methods, are stochastic and deterministic global optimization algorithms,

@@

in (Rios, L. M., Sahinidis, N. V., 2013), (Mongeau, M.,  Karsenty, H., Rouzé, V., Hiriart-Urruty, J. B., 2000), (Pintér, J. D., 2009), etc.
Nevertheless, even from such a short list the following conclusions can be drawn (see also Liberti, L., 2006):

@@

optimization aimed at developing efficient parallel algorithms for global search – see, for example, (Strongin, R. G., 1978), \cite{strSergGO}, (\cite{stronginGergelBarkalovParGO}).

@@

corresponding minimized function to satisfy the uniform Hölder condition (see Strongin, R. G., 1978, \cite{strSergGO}) i.e.

@@

The information-statistical theory of global search formulated in (Strongin, R. G., 1978), \cite{strSergGO}

@@

presented as follows --- see (Strongin, R. G., 1978), \cite{strSergGO}.

>>>>

\item GlobSol \cite{kearfott2009} is oriented towards solving global optimization problems as well as

@@

\item LINDO \cite{linSchrage2009} is features by a wide spectrum of problem solving mehtods which
it can be used for --- these include linear, integer, stochastic, nonlinear, and global

@@

problems (see, for example, \cite{iosoDescription}). The system is widely used to

@@

\item MATLAB Global Optimization Toolkit (see, for example, \cite{venkataraman2009}) includes a wide spectrum

@@

TOMLAB system (see, for example, \cite{holmstromEdvall2004}), which is an additional extension the widely-used MATLAB.

@@

integer programming and global optimization problems using the branch and bound method \cite{sahinidis1996}.
BARON is included in the GAMS (General Algebraic Modeling System) system used extensively – see \cite{bussieckMeeraus2004}.

@@

implemented in the R language (see, for example, \cite{mullen2014}). Among these methods, are stochastic and deterministic global optimization algorithms,

@@

in \cite{riosSahinidis2013}, \cite{mongeauKarsentyRouze2000}, \cite{pinter2009}, etc.
Nevertheless, even from such a short list the following conclusions can be drawn (see also \cite{liberti2009}):

@@

optimization aimed at developing efficient parallel algorithms for global search --- see, for example, \cite{strongin1978}, \cite{strSergGO}, (\cite{stronginGergelBarkalovParGO}).

@@

corresponding minimized function to satisfy the uniform Hölder condition (see \cite{strongin1978}, \cite{strSergGO}) i.e.

@@

The information-statistical theory of global search formulated in \cite{strongin1978}, \cite{strSergGO}

@@

presented as follows --- see \cite{strongin1978}, \cite{strSergGO}.
